Randomization Examples using `nycflights13` `flights` data

### 2017-12-27 inst/doc/flights_examples.Rmd
implement mean, prop and diff props on flights data.

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null <- fli_small %>%
  specify(response = dep_delay, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = p_hat, col = "red")
null %>%
  summarize(mean(stat > p_hat)) * 2
```

@@

```{r}
prof_small %>%
  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

>>>>

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = p_hat, col = "red")
null %>%
  summarize(mean(stat < p_hat)) * 2
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, col = "red")
null %>%
  summarize(mean(stat < d_hat)) * 2
```
